hbm_paper_results

### 2024-05-20 paper_lbcc_results.Rmd
exploratory sigma plots

@@

@@

```{r}
all.pred.df <- reduce(list(gmv.cf.gam.pred.df_full, gmv.cf.gamlss.pred.df_full, gmv.raw.pred.site.df, gmv.raw.pred.df), full_join)

@@

@@

```{r}
wmv.all.pred.df <- reduce(list(wmv.raw.pred.site.df, wmv.raw.pred.df, wmv.cf.gam.pred.site.df, wmv.cf.gam.pred.df, wmv.cf.gamlss.pred.site.df, wmv.cf.gamlss.pred.df), full_join)

@@

@@

```{r}
sgmv.all.pred.df <- reduce(list(sgmv.raw.pred.site.df, sgmv.raw.pred.df, sgmv.cf.gam.pred.site.df, sgmv.cf.gam.pred.df, sgmv.cf.gamlss.pred.site.df, sgmv.cf.gamlss.pred.df), full_join)

@@

See Ventricles
```{r}
#raw
ven.raw.mod <- readRDS(paste0(der_path, "/Ventricles_lifespan-CN-imp-sites-euler_raw_no.tbv_mod.rds"))
ven.raw.pred.df <- pred.across.ages.lbcc(ven.raw.mod, raw.data)
# ven.raw.mod.site <- readRDS(paste0(der_path, "/Ventricles_lifespan-CN-imp-sites-euler_raw_site.est_mod.rds"))
# ven.raw.pred.site.df <- pred.across.ages.lbcc.study(ven.raw.mod.site, raw.data)

# ven.raw.pred.site.df <- ven.raw.pred.site.df %>%
#   mutate(study_incl = TRUE,
#          combat= "raw")
ven.raw.pred.df <- ven.raw.pred.df %>%
  mutate(study_incl = FALSE,
         combat= "raw")

@@

```{r}
ven.all.pred.df <- reduce(list(ven.raw.pred.df, ven.cf.gam.pred.site.df, ven.cf.gam.pred.df, ven.cf.gamlss.pred.site.df, ven.cf.gamlss.pred.df), full_join) #ven.raw.pred.site.df

@@

>>>>

load ComBat-harmonized data
```{r}
cf.lm.data <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler_log-cf_cf.lm_batch.study_data.csv"))
gmv.cf.lm.mod <- readRDS(paste0(der_path, "/GMV_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_no.tbv_mod.rds"))

gmv.cf.lm.pred.df <- pred.across.ages.lbcc(gmv.cf.lm.mod, cf.lm.data)

gmv.cf.lm.pred.df %>%
  ggplot() +
  geom_line(aes(x=age_days, y=f.sigma), color="red") +
  geom_line(aes(x=age_days, y=m.sigma), color="blue")

gmv.cf.lm.mod.site <- readRDS(paste0(der_path, "/GMV_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_site.est_mod.rds"))

gmv.cf.lm.pred.site.df <- pred.across.ages.lbcc.study(gmv.cf.lm.mod.site, cf.lm.data)

gmv.cf.lm.pred.site.df %>%
  ggplot() +
  geom_line(aes(x=age_days, y=f.sigma), color="red") +
  geom_line(aes(x=age_days, y=m.sigma), color="blue")
```

```{r}
gmv.cf.lm.pred.site.df <- gmv.cf.lm.pred.site.df %>%
  mutate(study_incl = TRUE,
         combat= "combat")
gmv.cf.lm.pred.df <- gmv.cf.lm.pred.df %>%
  mutate(study_incl = FALSE,
         combat= "combat")

gmv.cf.lm.pred.df_full <- full_join(gmv.cf.lm.pred.site.df, gmv.cf.lm.pred.df)

gmv.cf.lm.pred.df_full %>%
  ggplot() +
  geom_line(aes(x=age_days, y=f.sigma, color=study_incl))
```

@@

gmv.cf.gamlss.mod.site$sigma.coefficients

@@

```{r}
all.pred.df <- reduce(list(gmv.cf.gam.pred.df_full, gmv.cf.lm.pred.df_full, gmv.cf.gamlss.pred.df_full, gmv.raw.pred.site.df, gmv.raw.pred.df), full_join)

@@

#combat
wmv.cf.lm.mod <- readRDS(paste0(der_path, "/wmv_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_no.tbv_mod.rds"))
wmv.cf.lm.pred.df <- pred.across.ages.lbcc(wmv.cf.lm.mod, cf.lm.data)

wmv.cf.lm.mod.site <- readRDS(paste0(der_path, "/wmv_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_site.est_mod.rds"))
wmv.cf.lm.pred.site.df <- pred.across.ages.lbcc.study(wmv.cf.lm.mod.site, cf.lm.data)

wmv.cf.lm.pred.site.df <- wmv.cf.lm.pred.site.df %>%
  mutate(study_incl = TRUE,
         combat= "combat")
wmv.cf.lm.pred.df <- wmv.cf.lm.pred.df %>%
  mutate(study_incl = FALSE,
         combat= "combat")

@@

```{r}
wmv.all.pred.df <- reduce(list(wmv.raw.pred.site.df, wmv.raw.pred.df, wmv.cf.gam.pred.site.df, wmv.cf.gam.pred.df, wmv.cf.gamlss.pred.site.df, wmv.cf.gamlss.pred.df, wmv.cf.lm.pred.site.df, wmv.cf.lm.pred.df), full_join)

@@

#combat
sgmv.cf.lm.mod <- readRDS(paste0(der_path, "/sgmv_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_no.tbv_mod.rds"))
sgmv.cf.lm.pred.df <- pred.across.ages.lbcc(sgmv.cf.lm.mod, cf.lm.data)

sgmv.cf.lm.mod.site <- readRDS(paste0(der_path, "/sgmv_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_site.est_mod.rds"))
sgmv.cf.lm.pred.site.df <- pred.across.ages.lbcc.study(sgmv.cf.lm.mod.site, cf.lm.data)

sgmv.cf.lm.pred.site.df <- sgmv.cf.lm.pred.site.df %>%
  mutate(study_incl = TRUE,
         combat= "combat")
sgmv.cf.lm.pred.df <- sgmv.cf.lm.pred.df %>%
  mutate(study_incl = FALSE,
         combat= "combat")

@@

```{r}
sgmv.all.pred.df <- reduce(list(sgmv.raw.pred.site.df, sgmv.raw.pred.df, sgmv.cf.gam.pred.site.df, sgmv.cf.gam.pred.df, sgmv.cf.gamlss.pred.site.df, sgmv.cf.gamlss.pred.df, sgmv.cf.lm.pred.site.df, sgmv.cf.lm.pred.df), full_join)

@@

See Ventricles
```{r}
#raw
ven.raw.mod <- readRDS(paste0(der_path, "/Ventricles_lifespan-CN-imp-sites-euler_raw_no.tbv_mod.rds"))
ven.raw.pred.df <- pred.across.ages.lbcc(ven.raw.mod, raw.data)

ven.raw.pred.df <- ven.raw.pred.df %>%
  mutate(study_incl = FALSE,
         combat= "raw")

#combat
ven.cf.lm.mod <- readRDS(paste0(der_path, "/Ventricles_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_no.tbv_mod.rds"))
ven.cf.lm.pred.df <- pred.across.ages.lbcc(ven.cf.lm.mod, cf.lm.data)

ven.cf.lm.mod.site <- readRDS(paste0(der_path, "/Ventricles_lifespan-CN-imp-sites-euler-log-cf-cf.lm-batch.study-data_site.est_mod.rds"))
ven.cf.lm.pred.site.df <- pred.across.ages.lbcc.study(ven.cf.lm.mod.site, cf.lm.data)

ven.cf.lm.pred.site.df <- ven.cf.lm.pred.site.df %>%
  mutate(study_incl = TRUE,
         combat= "combat")
ven.cf.lm.pred.df <- ven.cf.lm.pred.df %>%
  mutate(study_incl = FALSE,
         combat= "combat")

@@

```{r}
ven.all.pred.df <- reduce(list(ven.raw.pred.df, ven.cf.gam.pred.site.df, ven.cf.gam.pred.df, ven.cf.gamlss.pred.site.df, ven.cf.gamlss.pred.df, ven.cf.lm.pred.site.df, ven.cf.lm.pred.df), full_join) #ven.raw.pred.site.df

@@

Get predictions for sex-effects

```{r}
mean(comfam.cf.gam_VolGlob$estimates$gamma.star, na.rm=TRUE)
mean(comfam.cf.gamlss_VolGlob$estimates$gamma.star, na.rm=TRUE)
mean(comfam.cf.gam_VolReg$estimates$gamma.star, na.rm=TRUE)
mean(comfam.cf.gamlss_VolReg$estimates$gamma.star, na.rm=TRUE)
mean(comfam.cf.gam_CT$estimates$gamma.star, na.rm=TRUE)
mean(comfam.cf.gamlss_CT$estimates$gamma.star, na.rm=TRUE)
mean(comfam.cf.gam_SA$estimates$gamma.star, na.rm=TRUE)
mean(comfam.cf.gamlss_SA$estimates$gamma.star, na.rm=TRUE)

mean(abs(comfam.cf.gam_SA$estimates$delta.star - 1), na.rm=TRUE)
mean(abs(comfam.cf.gamlss_SA$estimates$delta.star - 1), na.rm=TRUE)
mean(abs(comfam.cf.gam_CT$estimates$delta.star - 1), na.rm=TRUE)
mean(abs(comfam.cf.gamlss_CT$estimates$delta.star - 1), na.rm=TRUE)
mean(abs(comfam.cf.gam_VolReg$estimates$delta.star - 1), na.rm=TRUE)
mean(abs(comfam.cf.gamlss_VolReg$estimates$delta.star - 1), na.rm=TRUE)
mean(abs(comfam.cf.gam_VolGlob$estimates$delta.star - 1), na.rm=TRUE)
mean(abs(comfam.cf.gamlss_VolGlob$estimates$delta.star - 1), na.rm=TRUE)
```
